Follow-up Samples

### 2017-05-03 submission/manuscript.tex

\textbf{\emph{The effects of treatment are not consistent across
treatment groups.}} We used two approaches to identify those bacterial
populations that change between the two samples for each diagnosis
group. First, we sought to identify individual OTUs that could account
for the change in overall community structure. However, using a paired
Wilcoxon test we were unable to identify any OTUs that were
significantly different in the pre and post-treatment groups {[}Figure
S1{]}. It is likely that high inter-individual variation and the
irregular distribution of OTUs across individuals limited the
statistical power of the test. To overcome these problems we developed
Random Forest models to identify collections of OTUs that would allow us
to differentiate between pre and post-treatment samples from each of the
diagnosis groups. Because of the relatively small number of subjects in
each group, we restricted our models to only incorporate 10 OTUs to
limit the likelihood that the models would overfit the data. Despite
this restriction, the models performed well (adenoma AUC range = 0.69 -
0.92, advanced adenoma AUC range = 0.80 - 1.00, carcinoma AUC range =
0.82 - 0.98). Interestingly, the 10 OTUs that were used for each model
had little overlap with each other {[}Figure 2{]}. These results support
the earlier community-wide analysis where we observed that the treatment
had an impact on the overall community structure; however, the effect of
treatment was not consistent across patients and diagnosis groups.

\textbf{\emph{Post-treatment samples from patients with carcinoma more
closely resemble those of a normal colon.}} Next, we determined whether
treatment changed the microbiota in a way that the post-treatment
communities resembled that of patients with normal colons. To test this,
we used an expanded cohort of 423 individuals that were diagnosed under
the same protocol as having normal colons or colons with adenoma,
advanced adenoma, or carcinoma {[}Table 2{]}. We then constructed Random
Forest models to classify the study samples, with the 3 diagnosis groups
(adenoma, advanced adenoma, or carcinoma), or having a normal colon. The
models performed well (adenoma AUC range =0.62 - 0.72, advanced adenoma
AUC range = 0.68 - 0.77, carcinoma AUC range = 0.84 - 0.90; Figure S2).
The OTUs that were incorporated into the adenoma and advanced adenoma
models largely overlapped and those OTUs that were used to classify the
carcinoma samples were largely distinct from those of the other two
models {[}Figure 3A{]}. Among the OTUs that were shared across the three
models were those populations generally considered beneficial to their
host (e.g. \emph{Faecalibacterium}, \emph{Lachnospiraceae},
\emph{Bacteroides}, \emph{Dorea}, \emph{Anaerostipes}, and
\emph{Roseburia}) {[}Figures 3B{]}. Although many of these OTUs were
also included in the model differentiating between patients with normal
colons and those with carcinoma, this model also included OTUs
affiliated with populations that have previously been associated with
carcinoma (\emph{Fusobacterium}, \emph{Porphyromonas},
\emph{Parvimonas}) {[}24--26{]} {[}Figure S3{]} with some individuals
showing are marked decrease in relative abundance {[}Figure S4{]}.
Finally, we applied these three models to the pre and post-treatment
samples for each diagnosis group and quantified the change in the
positive probability of the model. A decrease in the positive
probability would indicate that the microbiota more closely resembled
that of a patient with a normal colon. There was no significant change
in the positive probability for the adenoma or advanced adenoma groups
{[}Figure 4{]}. The positive probability for the pre and post-treatment
samples from patients diagnosed with carcinoma significantly decreased
with treatment, suggesting a shift toward a normal microbiota for most
individuals. Only, 6 of the 26 patients (23.08\%) who were diagnosed
with a carcinoma had a higher positive probability after treatment; one
of those was re-diagnosed with carcinoma on the follow up visit. These
results indicate that, although there were changes in the microbiota
associated with treatment, those experienced by patients with carcinoma
after treatment yielded gut bacterial communities of greater similarity
to that of a normal colon.

>>>>

\textbf{\emph{The effects of treatment are not consistent across
treatment groups.}} We used two approaches to identify those bacterial
populations that change between the two samples for each diagnosis
group. First, we sought to identify individual OTUs that could account
for the change in overall community structure. However, using a paired
Wilcoxon test we were unable to identify any OTUs that were
significantly different in the pre and post-treatment groups (P-value
\textless{}, \textless{}, \textless{}, \textless{}, \textless{},
\textless{}, \textless{}, \textless{}, \textless{}, \textless{},
\textless{}, \textless{}, \textless{}, \textless{}, \textless{},
\textless{}, \textless{}, \textless{}, \textless{}, \textless{},
\textless{}, \textless{}, \textless{}, \textless{}, \textless{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, NA, NA, NA, NA, NA, \textless{},
\textless{}, \textless{}, \textless{}, \textless{}, \textless{},
\textless{}, \textless{}, \textless{}, \textless{}, \textless{},
\textless{}, \textless{}, \textless{}, \textless{}, \textless{},
\textless{}, \textless{}, \textless{}, \textless{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{}, NA, NA,
NA, \textless{}, \textless{}, \textless{}, \textless{}, \textless{},
\textless{}, \textless{}, \textless{}, \textless{}, \textless{},
\textless{}, \textless{}, \textless{}, \textless{}, \textless{},
\textless{}, \textless{}, \textless{}, \textless{}, \textless{},
\textless{}, \textless{}, \textless{}, \textless{}, \textless{},
\textless{}, \textless{}, \textless{}, \textless{}, \textless{},
\textless{}, \textless{}, \textless{}, \textless{}, \textless{},
\textless{}, \textless{}, \textless{}, \textless{}, \textless{},
\textless{}, \textless{}, \textless{}, \textless{}, \textless{},
\textless{}, \textless{}, \textless{}, \textless{}, \textless{},
\textless{}, \textless{}, \textless{}, \textless{}, \textless{},
\textless{}, \textless{}, \textless{}, \textless{}, \textless{},
\textless{}, \textless{}, \textless{}, \textless{}, \textless{},
\textless{}, \textless{}, \textless{}, \textless{}, \textless{},
\textless{}, \textless{}, \textless{}, \textless{}, \textless{},
\textless{}, \textless{}, \textless{}, \textless{}, \textless{},
\textless{}, \textless{}, \textless{}, \textless{}, \textless{},
\textless{}, \textless{}, \textless{}, \textless{}, \textless{},
\textless{}, \textless{}, \textless{}, \textless{}, \textless{},
\textless{}, \textless{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
\textgreater{}, \textgreater{}, \textgreater{}, \textgreater{},
